### 2016-05-19 writing/latex/code.tex
Add changes to final section

>>>>

\subsubsection*{\texttt{classes.py}}
Contains the 220 equivalence classes of mesh patterns of length 2 shown in
% \ChapterRef{cha:equivs}.
\subsubsection*{\texttt{helper\_funcs.py}}
Contains functions to convert between different classes used in experimentation
as well as a class that functions as an accumulator.
\subsubsection*{\texttt{p\_rule.py}}
Contains functions that compute equivalences by the first and second dominating
rules, and functions that return coincidences not explained by the rules.
\subsubsection*{\texttt{wilf.py}}
Contains a class that functions as a counter for Wilf-equivalences based on
a dictionary, functions to calculate trivial Wilf classes and functions that
calculate Wilf-equivalences experimentally
\subsubsection*{\texttt{main.py}}
The main file to import that automatically runs all of the experimental setup
and calculations for coincidences and Wilf-equivalences.
\subsubsection*{\texttt{scratchpad.py}}
A collection of anonymous functions and utilities that do not fit into other
files.

### 2016-05-19 writing/latex/confut.tex
Add changes to final section

\chapter{Conclusions and Future work}
\nextvar
From \ChapterRef{chap:coincs} it can be seen that automatically classifying
coincidences of mesh patterns is a difficult task, establishing rules for longer
dominating patterns requires many more cases to be taken. It would however
be interesting to consider the application of the third Dominating Rule to mesh
patterns without any dominating pattern in order to try to capture some of the
coincidences described in\textcite{DBLP:journals/combinatorics/HilmarssonJSVU15}
 and \textcite{DBLP:journals/corr/ClaessonTU14}.
It is not possible to apply the first and second Dominating Rules to the pattern
itself, since when applying the rules we consider containers of the pattern inside
the avoiders of the dominating pattern. For example if we were to attempt to apply
the first rule to the pattern \(\perm{1,2}\) then we would have to consider
containers of \(\perm{1,2}\) inside \(\av{\perm{1,2}}\), and obviously this can
never occur.

@@

It would be interesting to consider a systematic explanation of Wilf-equivalences
amongst classes where \(\perm{3,2,1}\) is the dominating pattern using the
construction presented in \cite[Sec.~12]{2015arXiv151203226B}, in order to directly
reach enumeration and hopefully establish some of the non-trivial Wilf-equivalences
between classes with different dominating patterns. For example, it is possible to show that
the sets \(\scriptvar = \av{\left\{\textpattern{}{1,2}{1/2,2/0,0/0,1/0,1/1,2/1},\perm{2,3,1}\right\}}\)\nextvar and
\(\scriptvar = \av{\left\{\textpattern{}{1,2}{1/2,2/0,0/0,1/0,1/1,2/1},\perm{3,2,1}\right\}}\), are Wilf-equivalent.
This can be seen by considering an occurrence of the mesh pattern,
\(p=\textpattern{}{1,2}{1/2,2/0,0/0,1/0,1/1,2/1}\) in a permutation
\begin{equation*}
    \raisebox{0.6ex}{
    \begin{tikzpicture}[scale=1, baseline=(current bounding box.center)]
        \draw (0.5,1.5) node {\(b_1\)};
        \draw (0.5,2.5) node {\( b_2\)};
        \draw (2.5,2.5) node {\( b_3\)};
        \modpattern[2]{2}{1,2}{0/0,1/0,1/1,1/2,2/0,2/1}
    \end{tikzpicture}
    }
\end{equation*}

>>>>

\chapter{Conclusions and Future work}
\nextvar
% From \ChapterRef{chap:coincs} it can be seen that automatically classifying
% coincidences of mesh patterns is a difficult task, establishing rules for longer
% dominating patterns requires many more cases to be taken.
If we consider a similar system for dominating patterns of length \(4\) and
mesh patterns of length \(2\), it can be seen that the number of cases required
to establish rules increases to a number that is infeasible to compute manually.
For an extension of the First Dominating rule alone, we would have to consider
placement of points in any pair of unshaded regions. The fact that the rules
established do not completely cover the coincidences with a dominating pattern
of length \(3\) (see \TableRef{tab:domclasses}) shows that this is a difficult
task.

It is interesting to consider the application of the Third Dominating rule,
as well as the simple extension of allowing a sequence of \texttt{add\_point}
operations, to meshpatterns without any dominating pattern in order to try to
capture some of the coincidences described in
\textcite{DBLP:journals/combinatorics/HilmarssonJSVU15}
 and \textcite{DBLP:journals/corr/ClaessonTU14}.
 \begin{example}
   We can establish the coincidence between the patterns
   \begin{equation*}
     m_1 = \pattern{}{1,2}{0/1,0/2,1/1,1/2,2/0}, \text{ and } m_2 = \pattern{}{1,2}{0/2,1/0,1/1,2/0,2/1}
   \end{equation*}
   That is not explained by the methods presented by \textcite{DBLP:journals/corr/ClaessonTU14}.

   Consider a permutation containing \(m_1\),
   \begin{equation*}
     \begin{tikzpicture}[scale=0.5]
         \modpattern[5]{}{1,2}{0/1,0/2,1/1,1/2,2/0}
         \draw (1.5,0.5) node {\(Y\)};
         \draw (2.5,1.5) node {\(X\)};
     \end{tikzpicture}
   \end{equation*}
   If the regions corresponding to both \(X\) and \(Y\) are empty then we have
   an occurrence of \(m_2\).
   Consider if the region corresponding to \(X\) is non-empty, we can then choose
   the lowest valued point in this region
   \begin{equation*}
     \begin{tikzpicture}[scale=0.5]
         \modpattern[5]{1,3}{1,3,2}{0/1,0/2,0/3,1/1,1/2,1/3,2/0,2/1,3/0,3/1}
         \draw (1.5,0.5) node {\(Y\)};
     \end{tikzpicture}
   \end{equation*}
   If the region corresponding to \(Y\) is empty then we have an occurrence of
   \(m_2\) with the indicated points.
   Now if the region corresponding to \(Y\) is non-empty, we can choose the
   rightmost point in this region.
   \begin{equation*}
     \begin{tikzpicture}[scale=0.5]
         \modpattern[5]{2,4}{2,1,4,3}{0/2,0/3,0/4,1/2,1/3,1/4,2/0,2/1,2/2,2/3,2/4,3/0,3/1,3/2,4/0,4/1,4/2}
     \end{tikzpicture}
   \end{equation*}
   And now the two indicated points form an occurrence of \(m_2\).
   We have therefore shown that any occurrence of \(m_1\) is an occurrence of
   \(m_2\) and we can easily show the converse by the same reasoning, so \(m_1\)
   and \(m_2\) are coincident.
   This is captured by an extension of the Third Dominating rule where we allow
   multiple steps of adding points before we check for subpattern containment.
 \end{example}
It is not possible to apply the first and second Dominating Rules to the pattern
itself, since when applying the rules we consider containers of the pattern inside
the avoiders of the dominating pattern. For example if we were to attempt to apply
the first rule to the pattern \(\perm{1,2}\) then we would have to consider
containers of \(\perm{1,2}\) inside \(\av{\perm{1,2}}\), and obviously this can
never occur.

@@

It would be interesting to consider a systematic explanation of Wilf-equivalences
amongst classes where \(\perm{3,2,1}\) is the dominating pattern, possible using the
construction presented in \cite[Sec.~12]{2015arXiv151203226B}, in order to directly
reach enumeration and hopefully establish some of the non-trivial Wilf-equivalences
between classes with different dominating patterns. For example, it is possible to show that
the sets \(\scriptvar = \av{\textpattern{}{1,2}{1/2,2/0,0/0,1/0,1/1,2/1},\perm{2,3,1}}\)\nextvar and
\(\scriptvar = \av{\textpattern{}{1,2}{1/2,2/0,0/0,1/0,1/1,2/1},\perm{3,2,1}}\), are Wilf-equivalent.
This can be seen by considering an occurrence of the mesh pattern,
\(p=\textpattern{}{1,2}{1/2,2/0,0/0,1/0,1/1,2/1}\) in a permutation
\begin{equation*}
    \raisebox{0.6ex}{
    \begin{tikzpicture}[scale=1, baseline=(current bounding box.center)]
        \draw (0.5,1.5) node {\(b_1\)};
        \draw (0.5,2.5) node {\( b_2\)};
        \draw (2.5,2.5) node {\( b_3\)};
        \modpattern[2]{2}{1,2}{0/0,1/0,1/1,1/2,2/0,2/1}
    \end{tikzpicture}
    }
\end{equation*}
